Evolutionary Design of Particles for Collectively Intelligent Problem Solving

### 2014-05-08 docs/paper.tex
Start evolution subsection of paper

>>>>

The evolution of a finite state machine for movement control was achieved through the application of a simple set of genetic operators to the weights and parameters of the machine. The genotype of a movement controller was represented as two integers, one for each guarding threshold, and a vector of real-valued numbers consisting of the alpha parameter, radius, and weight given to each component of each compound movement behavior.

The set of states in each controller was fixed to be the same set of compound behaviors as those found in \cite{rodriguez2004extending}, but with parameters derived through evolutionary programming. This allowed for easy comparison with the authoritative, human-derived solution. In addition, the transitions between states were kept the same except for the guarding thresholds, which were evolved.

New individuals were introduced through the application of mutation and recombination operators. The mutation operator adds or removes an integer value from each selected threshold and adds a uniformly distributed random value with mean 0 to each selected real-valued parameter. Each mutation operation selects which parameters to modify independently, so the mutation of one parameter is independent of the mutation of another parameter.
